Capstone Movielens Report

### 2025-11-18 reports/capstone-movielens.site/05.appendix.Rmd
Update: Describing helper function (in progress): model.tune.param_range.

::: {.noteblock data-latex=""}
In the function body, the *step size* is stored in the local variable `seq_increment`, and the values of $\start$, $\end$, and $\dvs$ are stored in the local variables `seq_start`, `seq_end`, and `interval_divisor`, respectively.
:::

@@

  2. Checks if the *step size* of the generated sequence is less than the minimum allowed value (in the current implementation, we use `1e-13`), and if `TRUE`, breaks out of the loop:
```{r eval=FALSE}
    if (seq_increment < 0.0000000000001) {
      warning("Function `model.tune.param_range`:
parameter value increment is too small.")

@@

  3. Creates a vector containing a sequence of $\lambda$ values generated as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above.

  2. Calls the [tune.model_param](#func.tune.model_param) function, passing the vector created in the previous step to the [param_values](#func.tune.model_param.args.param_values) argument (along with the values of the other arguments) of the `tune.model_param` function.

>>>>

::: {.noteblock data-latex=""}
In the function body, the *step size* is stored in the local variable `seq_increment`, and the values of $start$, $end$, and $dvs$ are stored in the local variables `seq_start`, `seq_end`, and `interval_divisor`, respectively.
:::

@@

  2. Checks if the *step size* of the generated sequence is less than the minimum allowed value (in the current implementation, we use `1e-13`), and if `TRUE`, breaks out of the loop. Otherwise, the execution continues to the next step:
```{r eval=FALSE}
    if (seq_increment < 0.0000000000001) {
      warning("Function `model.tune.param_range`:
parameter value increment is too small.")

@@

  3. If the *step size* is no less than the minimum allowed value (`seq_increment >= 1e-13` in our case) creates a vector containing a sequence of $\lambda$ values generated as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above:
```{r eval=FALSE}
    test_param_vals <- seq(seq_start, seq_end, seq_increment)
```

  4. Calls the [tune.model_param](#func.tune.model_param) helper function, passing the vector created in the previous step to the [param_values](#func.tune.model_param.args.param_values) argument (along with the values of the other arguments of the function `tune.model_param`).
